The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, ...

### 2011-12-19 bmc_article.tex
Use biblatex
Written a draft abstract

% Load packages
\usepackage{cite} % Make references as [1-4], not [1,2,3,4]
\usepackage{url}  % Formatting web addresses  
\usepackage{ifthen}  % Conditional 
\usepackage{multicol}   %Columns
\usepackage[utf8]{inputenc} %unicode support
%\usepackage[applemac]{inputenc} %applemac support if unicode package fails
%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails
\urlstyle{rm}

@@

\title{The Chemistry Development Kit (CDK). 3. Atom typing, ...}

@@

\author{
  Egon L Willighagen\correspondingauthor$^{1}$%
  \email{Egon L Willighagen\correspondingauthor - egon.willighagen@gmail.com}
\and
  Christoph Steinbeck\correspondingauthor$^2$%
  \email{Christoph Steinbeck\correspondingauthor - steinbeck@ebi.ac.uk}
}

@@

\address{
    \iid(1)Life Sciences Department, Kings College London, Cornwall House,
        Waterloo Road, London, UK\\
    \iid(2)Department of Zoology, Cambridge, Waterloo Road, London, UK
}

@@

\begin{abstract}
        % Do not use inserted blank lines (ie \\) until main body of text.
        \paragraph*{Background:} Text for this section of the abstract.

        \paragraph*{Results:} Text for this section of the abstract \ldots

        \paragraph*{Conclusions:} Text for this section of the abstract \ldots
\end{abstract}

@@

@@

@@

{\ifthenelse{\boolean{publ}}{\footnotesize}{\small}
 \bibliographystyle{bmc_article}  % Style BST file
  \bibliography{bmc_article} }     % Bibliography file (usually '*.bib' )

>>>>

% Load packages
\usepackage{url}  % Formatting web addresses  
\usepackage{ifthen}  % Conditional 
\usepackage{multicol}   %Columns
\usepackage[utf8]{inputenc} %unicode support
%\usepackage[applemac]{inputenc} %applemac support if unicode package fails
%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails
\urlstyle{rm}
\usepackage[citestyle=numeric-comp]{biblatex}                                                                     
\setlength{\bibitemsep}{0cm}                                                                                                                
\renewbibmacro{in:}{%                                                                                                                       
  \ifentrytype{article}{}{%                                                                                                                 
  \printtext{\bibstring{in}\intitlepunct}}}                                                                                                 
\addbibresource{bmc_article.bib}

@@

\title{The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, ...}

@@

\author{
  Egon L Willighagen$^{1}$% // FIXED FIRST AUTHOR
  \email{Egon L Willighagen - egon.willighagen@ki.se}
\and
  Miguel Rojas Cherto$^2$%
  \email{Miguel Rojas Cherto - steinbeck@ebi.ac.uk}
\and
  You C B Here$^3$%
  \email{You C B Here - you.here@example.org}
\and
  C D K Project\correspondingauthor$^98$% // FIXED SECOND BUT LAST AUTHOR
  \email{C D K Project - cdk-devel@lists.sourceforge.net}
\and
  Rajarshi Guha$^99$% // FIXED ONE BUT LAST AUTHOR
  \email{Rajarshi Guha - steinbeck@ebi.ac.uk}
\and
  Christoph Steinbeck$^100$% // FIXED LAST AUTHOR
  \email{Christoph Steinbeck - steinbeck@ebi.ac.uk}
}

@@

\address{
    \iid(1)Division of Molecular Toxicology, Institute of Environmental Medicine, Karolinska Institutet, SE-17177 Stockholm, Sweden\\
    \iid(2)Division of Analytical Biosciences, Leiden/Amsterdam Center for Drug Research, Leiden, The Netherlands \\
    \iid(3)Example Ltd., Glasgow, UK \\
    \iid(98)\url{http://cdk.sourceforge.net/} \\
    \iid(99)NIH Center for Translational Therapeutics, 9800 Medical Center Drive, Rockville, MD 20878, USA \\
    \iid(100)Chemoinformatics and Metabolism team, European Bioinformatics Institute, Hinxton, UK 
}

@@

\begin{abstract}
% Do not use inserted blank lines (ie \\) until main body of text.
\paragraph*{Background:}
Cheminformatics is a well-established field with many applications in chemistry,
drug discovery, and the life sciences. Particularly in the latter field, however,
molecular properties are not well-understood yet, and the interaction between
molecules and larger systems remains a challenge to be modeled. Therefore, the
development of new data mining and pattern recognition continues to be important
and the need for access to a cheminformatics library that one can change remains.

\paragraph*{Results:}
We here report the 1.4 series of the Chemistry Development Kit and outline how
it evolved since the previous report. We demonstrate the new APIs we introduced
in this version and discuss the extensive quality control mechanism we have
adopted. New APIs have been introduced for substructure searching, rendering of
molecules, handling of molecular formulas, atom type perception, and InChI
support. At a quality control side we have introduced automated building,
extensive unit and use case testing, and adopted peer review.

\paragraph*{Conclusions:}
With this paper we have shown the continued effort to provide a free, Open Source
cheminformatics library, and show that such colleborative projects can survive for
a long period. We have taken advantage from the community support, and show
that an open source cheminformatics project can act as a peer reviewed
publishing platform for scientific computating software.
\end{abstract}

@@

  \subsubsection*{Rendering API}

  Initiated by ...

  \subsubsection*{Molecular Formula}

  ....

  \subsubsection*{SMARTS parser}

  ....

  \subsubsection*{Partial charges and Delocalization}

  ....

  \subsubsection*{New Builders}

  ....

  \subsubsection*{InChI integration}

  .... jni-inchi dep, atom numbering, tautomer generation

@@

  \subsubsection*{Peer review}

  \subsubsection*{Modularization}

  \subsubsection*{Documentation}

  Initially done with DocCheck, replaced by OpenJavaDocCheck ...

  \subsubsection*{Unit testing}

  \subsubsection*{Code Quality}

  PMD ...

  \subsubsection*{Git, branching, and patches}

@@

{\ifthenelse{\boolean{publ}}{\footnotesize}{\small}
\printbibliography
}
